# Cookbook

This codebook was generated on 
```{r echo=FALSE}
Sys.Date()
```


## Variable list and descriptions

Variable Name | Description|
------------- | ------------|
subject | ID the subject who performed the activity for each window sample. Its range is from 1 to 30.|
activity | Activity Name|
MEAN - tBodyAcc-X | Mean of tBodyAcc-X|
MEAN - tBodyAcc-Y | Mean of tBodyAcc-Y
MEAN - tBodyAcc-Z | Mean of tBodyAcc-Z
STD - tBodyAcc-X  | Standard Deviation of tBodyAcc-X
STD - tBodyAcc-Y  | Standard Deviation of tBodyAcc-Y
STD - tBodyAcc-Z  | Standard Deviation of tBodyAcc-Z

### Additional Variables


MEAN - tGravityAcc-X
MEAN - tGravityAcc-Y
MEAN - tGravityAcc-Z
STD - tGravityAcc-X        
STD - tGravityAcc-Y
STD - tGravityAcc-Z
MEAN - tBodyAccJerk-X      
MEAN - tBodyAccJerk-Y
MEAN - tBodyAccJerk-Z       
STD - tBodyAccJerk-X       
STD - tBodyAccJerk-Y        
STD - tBodyAccJerk-Z        
MEAN - tBodyGyro-X
MEAN - tBodyGyro-Y          
MEAN - tBodyGyro-Z          
STD - tBodyGyro-X          
STD - tBodyGyro-Y           
STD - tBodyGyro-Z           
MEAN - tBodyGyroJerk-X     
MEAN - tBodyGyroJerk-Y      
MEAN - tBodyGyroJerk-Z      
STD - tBodyGyroJerk-X      
STD - tBodyGyroJerk-Y       
STD - tBodyGyroJerk-Z       
MEAN - tBodyAccMag         
STD - tBodyAccMag           
MEAN - tGravityAccMag       
STD - tGravityAccMag       
MEAN - tBodyAccJerkMag      
STD - tBodyAccJerkMag       
MEAN - tBodyGyroMag        
STD - tBodyGyroMag          
MEAN - tBodyGyroJerkMag     
STD - tBodyGyroJerkMag     
MEAN - fBodyAcc-X           
MEAN - fBodyAcc-Y           
MEAN - fBodyAcc-Z          
STD - fBodyAcc-X            
STD - fBodyAcc-Y            
STD - fBodyAcc-Z
MEAN - fBodyAccJerk-X       
MEAN - fBodyAccJerk-Y       
MEAN - fBodyAccJerk-Z      
STD - fBodyAccJerk-X        
STD - fBodyAccJerk-Y        
STD - fBodyAccJerk-Z       
MEAN - fBodyGyro-X          
MEAN - fBodyGyro-Y          
MEAN - fBodyGyro-Z         
STD - fBodyGyro-X           
STD - fBodyGyro-Y           
STD - fBodyGyro-Z          
MEAN - fBodyAccMag          
STD - fBodyAccMag           
MEAN - fBodyBodyAccJerkMag 
STD - fBodyBodyAccJerkMag   
MEAN - fBodyBodyGyroMag     
STD - fBodyBodyGyroMag



## Show a few rows of the dataset


```{r echo=TRUE}
source("run_analysis.R")
head(run_analysis())
```

## Save to file

Save data table objects to a tab-delimited text file called Result.txt

#### Additional Information

```{r echo = TRUE}
Sys.Date()
sessionInfo()
```
